### 2020-07-28 draft.Rmd
cleaned up table output, fixed an error in the test we were using for pairwise comparison matrix

alpha = 0.05
adjusted_alpha = 2*alpha/ (k*(k-1))
print(sprintf("Alpha of %s leads to an adjusted alpha of %s", alpha, adjusted_alpha))

crit_alpha = calculate_critical(sample_q, alpha)
crit_adj = calculate_critical(sample_q, adjusted_alpha)
crit_message = sprintf("critical values of significance levels %s and %s are %s and %s respectively", alpha, adjusted_alpha, crit_alpha, crit_adj)
print(crit_message)

@@

for (row in names(treat_list)){
  for(col in names(treat_list)){
    m[row,col] = mw_stat(treat_list[[row]], treat_list[[col]])
  }
}
print("pairwise statistics greater than or equal to the adjusted alpha critical value")
print(m >= crit_adj)

>>>>

alpha = 0.05
adjusted_alpha = 2*alpha/ (k*(k-1))

crit_alpha = calculate_critical(sample_q, alpha)
crit_adj = calculate_critical(sample_q, adjusted_alpha)
# crit_message = sprintf("critical values of significance levels %s and %s are %s and %s respectively", alpha, adjusted_alpha, crit_alpha, crit_adj)
# print(crit_message)

@@

for (row in names(treat_list)){
  for(col in names(treat_list)){
    m[row,col] = wilcox.test(
      treat_list[[row]],
      treat_list[[col]],
      alternative="greater")$p.value
  }
}
#print("pairwise statistics greater than or equal to the adjusted alpha critical value")
comparison_matrix = as.table(m <= adjusted_alpha)
knitr::kable(comparison_matrix, caption="Significant difference found in pairwise comparison.")
